Exploring the Design Space of Differentially Private Bayesian Inference under Hellinger Distance

### 2019-01-21 ICML2019/main.tex
pass section 4

\section{Private Mechanisms}
\label{sec_mechs}
\subsection{Calibrating noise w.r.t. $\ell_1$ norm ($\lapmech$)}
We start off by presenting a mechanism based on the Laplace primitive.
The mechanism, denoted by $\lapmech$, takes in input the data $\dataobs$, a mechanism, $\bysinfer$, that is used to perform inference on some parameter,
a prior and a likelihood function, and the $\epsilon$ parameter measuring the privacy level.
Now, $\lapmech(\dataobs,\bysinfer, \mathsf{prior}, \mathsf{likelihood}, \epsilon)$,
simply adds Laplace noise to the parameters of the posterior distributions. The mechanisms also performs a
post-processing phase by flooring and  truncating the noisy parameters so that they belong to the right interval.
In the case of the Beta-Binomial model the output produced is: $\betad(\alpha +  \lfloor{\Delta \alpha + \eta}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + \eta}\rfloor^n_0)$
with $\eta \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$, where $\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into
$[0,n]$. This mechanism is described by the pesudocode in Figure \ref{mech:lapmech}.\\
Since we are adding noise directly to the parameters, the sensitivity should be calibrated w.r.t $\ell_1$-norm. That is,
the sensitivity is defined as:
\[
   \Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1
\]
This value can be quickly seen as being upper bounded by  the dimensionality. (e.g. 2 for the Beta-Binomial model and  $k$ for
the Dirichlet-Multinomial model).
  \begin{algorithm}
  \caption{$\lapmech$ for the Beta-Binomial model}
  \label{mech:lapmech}
  \begin{algorithmic}
  \INPUT observed data set $\dataobs \in \{0,1\}^n$, inference algorithm: $\bysinfer$, 
  prior: $\betad(\alpha, \beta)$, likelihood: $\binomial{n}{\theta}$, $\epsilon$
  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$.  
  \STATE \quad  $\eta \sim \lap{0}{\frac{2}{\epsilon}}$.
  \STATE \quad  $\tilde{\alpha}=\alpha + \lfloor{(\alpha' - \alpha) + \eta}\rfloor^n_0$ 
  \STATE \quad  $\tilde{\beta}=\beta + n - \lfloor{(\alpha' - \alpha) + \eta}\rfloor^n_0$ \\
  % \RETURN $a_{k+1}$.
  \noindent {\bf return} $\betad(\tilde{\alpha}, \tilde{\beta})$
  \end{algorithmic}
  \end{algorithm}

>>>>

\section{Private Mechanisms}
\label{sec_mechs}
In this section we will describe and analyse a series of mechanisms.
Section \ref{sec_ell1_dim} presents a first mechanism called $\lapmech$ based on the Laplace primitive
where the sensitivity is measured w.r.t. to $\ell_1$ norm.
We will then notice, Section \ref{??}, that this mechanism's accuracy can be improved by performing a better analysis on
the sensitivity of the inference process.
Section \ref{???}, shows an instance of the exponential mechanism where the scoring
function is based on the Hellinger distance, we will see how this mechanisms performs
poorly due to the very high global sensitivity of the inference process w.r.t to this metric.
Section \ref{???}
\subsection{Calibrating noise w.r.t. $\ell_1$ norm ($\lapmech$)}
\label{sec_ell1_dim}
We start off by presenting a mechanism based on the Laplace primitive.
The mechanism, denoted by $\lapmech$, takes in input the data $\dataobs$, a mechanism, $\bysinfer$, that is used to perform inference on some parameter,
a prior and a likelihood function, and the $\epsilon$ parameter measuring the privacy level.
Now, $\lapmech(\dataobs,\bysinfer, \mathsf{prior}, \mathsf{likelihood}, \epsilon)$,
simply adds Laplace noise to the parameters of the posterior distributions. The mechanisms also performs a
post-processing phase by flooring and  truncating the noisy parameters so that they belong to the right interval.
In the case of the Beta-Binomial model the output produced is: $\betad(\alpha +  \lfloor{\Delta \alpha + \eta}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + \eta}\rfloor^n_0)$
with $\eta \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$, where $\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into
$[0,n]$. This mechanism is described by the pesudocode in Figure \ref{mech:lapmech}.\\
Since we are adding noise directly to the parameters, the sensitivity should be calibrated w.r.t $\ell_1$-norm. That is,
the sensitivity is defined as:
\[
   \Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1
\]
This value can be quickly seen as being upper bounded by  the dimensionality. (e.g. 2 for the Beta-Binomial model and  $k$ for
the Dirichlet-Multinomial model).
  \begin{algorithm}
  \caption{$\lapmech$ for the Beta-Binomial model}
  \label{mech:lapmech}
  \begin{algorithmic}
  \INPUT observed data set $\dataobs \in \{0,1\}^n$, inference algorithm: $\bysinfer$, 
  prior: $\betad(\alpha, \beta)$, likelihood: $\binomial{n}{\theta}$, $\epsilon$
  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$.  
  \STATE \quad  $\eta \sim \lap{0}{\frac{2}{\epsilon}}$.
  \STATE \quad  $\tilde{\alpha}=\alpha + \lfloor{(\alpha' - \alpha) + \eta}\rfloor^n_0$ 
  \STATE \quad  $\tilde{\beta}=\beta + n - \lfloor{(\alpha' - \alpha) + \eta}\rfloor^n_0$ \\
  % \RETURN $a_{k+1}$.
  \noindent {\bf return} $\betad(\tilde{\alpha}, \tilde{\beta})$
  \end{algorithmic}
  \end{algorithm}
